# Classification

```{r, message=FALSE, warning=FALSE}
plkt <- data.io::read(here::here("data", "mesoplankton.csv"))
```

This guide uses a classification divided into 6 levels

-   N1 : quick and convenient separation into `r length(unique(plkt$N1))` groups. The groups are as follows: `r unique(plkt$N1)` .

-   N2 : Separation mainly on the basis of phyla into `r length(unique(plkt$N2))` groups

-   N3 : Separation mainly on the basis of Class into `r length(unique(plkt$N3))` groupes

-   N4 : Separation on the basis of Orders (if possible) into `r length(unique(plkt$N4))` groups

-   N5 : Separation on the basis of Sub-orders and Genres into `r length(unique(plkt$N5))` groups

-   N6 : Separation on the basis of species into `r length(unique(plkt$N6))` groups

The tree structure of the different groups can be viewed below. A mindmap view is also available [here](https://coggle.it/diagram/XniwI-MesP8BdYNn/t/mesoplankton/46c9eaed5e2a5c6a3292935cfdb71acaf585976bef9c390b482e2f473c587862?present=1).

```{r}
fs::dir_tree("training_set/", type = "directory")
```

Planktonic organisms are available in the form of vignettes. It is therefore only possible to classify individuals on the basis of morphological criteria.

The first level of classification in this guide corresponds more or less to level 1 or 2 of this classification. The second level of classification corresponds mainly to level 3 of the tree presented above. The third level corresponds to the most detailed classification.
